\documentclass{tccv}
\usepackage[english]{babel}
\usepackage{enumitem}


\begin{document}

\part{Sorawee Porncharoenwase}

\section{Jobs and Works}

\begin{eventlist}

\item{2015 -- Present}
     {Brown CS}
     {Teaching Assistant}
     
\begin{yearlist}

\item{Spring 2015}
     {Course Staff}
     {Coursera: Coding the Matrix}

\item{Fall 2015}
		 {Teaching Assistant}
		 {CS019 Accelerated Intro to CS}

\item{Spring 2016}
		 {Teaching Assistant}
		 {CS195Y Logic for Systems}

\item{Fall 2016}
		 {Head Teaching Assistant}
		 {CS053 Coding the Matrix}	   

\item{Spring 2017}
	   {Head Teaching Assistant}
	   {CS195Y Logic for Systems}	 
	   
\item{Fall 2017}
		 {Teaching Assistant}
	   {CS173 Intro to Prog. Languages}	 

\item{Spring 2018}
		 {Teaching Assistant}
		 {CS195Y Logic for Systems}	 
\end{yearlist}

\item{2015 -- Present}
     {Bootstrap and Brown CS}
     {Contributor}
     
Work on chart library integration and compiler optimization for Pyret, a teaching programming language for Bootstrap, a CS curricular program for high school students used in at least 17 states in the U.S., and Brown University courses.

\item{June -- August 2016}
{Facebook, Inc.}
{Summer Intern (Release Engineer)}

Developed a framework to automate Facebook \newline mobile app uploading to app stores.

\item{June -- August 2015}
{Square, Inc.}
{Summer Intern (Platform Engineer)}

Designed a domain-specific language for a database migration tool.

\end{eventlist}

\section{Awards \& Honors}

\begin{yearlist}
	\item{December 2017}
	{Honorable Mention}
	{CRA Outstanding\newline Undergraduate\newline Researcher Award}
	\item{March 2017}
	{The Randy F. Pausch CS Undergrad Summer \newline Research Award }
	{Brown CS}
	\item{February 2014}
	{Excellence Award}
	{VEX Robotics Competition, East Rockaway, NY}
	\item{September 2012}
	{Bronze Medal}
	{International Olympiad in Informatics, Italy}
\end{yearlist}

\personal
[www.sorawee.com]
{Box 4183, Brown University\newline Providence, RI, USA}
{(914) 920 1166}
{sorawee.pwase@gmail.com}

\section{Research}

\begin{eventlist}
	\item{June -- August 2017}
	{Brown CS}
	{CompoSAT: Specification-Guided \newline Coverage for Scenario Finding}
	
	with Tim Nelson and Shriram Krishnamurthi
	
	\vspace{3mm}
	
	Wrote a paper (under submission) and developed an extension to model finders, tools that help users to explore a system's behavior. 
	
\end{eventlist}

\section{Education}

\begin{yearlist}
	
	\item[Candidate for Bachelor of Science in Computer Science (Unofficial GPA: 3.93/4)]{April 2018}
	{Brown University}
	{Providence, RI}
	
	
	\item{June 2014}
	{The Masters School}
	{Dobbs Ferry, NY}
	
	\item{March 2012}
	{Triam Udom Suksa School}
	{Bangkok, Thailand}
	
\end{yearlist}


\section{Experience}

\begin{eventlist}

\item{2016 -- Present}
     {Thai Government}
		 {Programmer}
		 
Maintain a server to generate necessary official documents for Thai students who receive a \\scholarship to study in the U.S.

\item{2013 -- Present}
{Thai Wikipedia}
{Administrator}

Maintain and help technical problems arise in Thai Wikipedia.

\item{2012 -- 2014}
     {MediaWiki and Pywikibot}
     {Contributor}
     
Contributed to the open-source projects.

\item{2012 -- 2016}
     {programming.in.th}
     {Development Staff}

Wrote programming contest tasks and maintained  programming.in.th, the largest programming \newline (contest) community in Thailand.

%\item{2010 -- 2011}
%     {Online Registration System\\Triam Udom Suksa School}
%     {Programmer and Manager}  
%  
%Proposed the online registration system for school applications to the school committee. Codeveloped the registration website, eventually served more than 13,000 students who applied to the school.

\end{eventlist}


%\section{Selected Coursework}
%
%\begin{description}
%	\itemsep0em 
%	\oitem CS273/298SK Programming Language Theory
%	\oitem CS195Y Logic for Systems
%	\oitem PHIL1885 Incompleteness
%	\oitem CS250B Optimization Algorithms for Planar Graphs
%\end{description}


\end{document}
